Implementing Real-time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
Adds references

The Internet architecture, in principle, allows free innovation at the
transport layer, provided the underlying network (IP) layer is unchanged.  
Routers should inspect the source addresses of packets to perform network
ingress filtering \cite{RFC2827}, and the destination addresses to route
packets to the correction destination, but should not inspect their
contents. This is not, of course, how the real network operates.

@@

UDP is the obvious base for future protocol development, since it provides
minimal additional services over the IP layer, allowing great flexibility
in innovation for protocols tunnelled on top. Provided middleboxes do not
inspect the payload too carefully, the only real cost to innovation, when
compared to a native transport protocol running over IP, is a few bytes of
additional header. Examples in this space include RTP \cite{RFC3550}, one
of the most widely deployed real-time transport protocols; the WebRTC Data
Channel \cite{}, which tunnels peer-to-peer SCTP associations over a DTLS
association over UDP; and QUIC \cite{}, which provides a modern alternative 
to TCP, implemented over UDP.

@@

Evidence that these services can be deployed above UDP exists in the form
of the WebRTC data channel \cite{}.  
\todo{expand}

@@

Taken together, the wide experiences with the WebRTC Data Channel and QUIC
demonstrate that the transport services necessary to support real-time
traffic could be deployed running over UDP. Our work prototyping the TCP
Hollywood protocol, and earlier measurements by Honda \emph{et al}.\
\cite{} also suggest that deployment over TCP is possible.

>>>>

The Internet architecture, in principle, allows free innovation at the
transport layer, provided the underlying network (IP) layer is unchanged.  
Routers should inspect the source addresses of packets to perform network
ingress filtering \cite{rfc:2827}, and the destination addresses to route
packets to the correction destination, but should not inspect their
contents. This is not, of course, how the real network operates.

@@

UDP is the obvious base for future protocol development, since it provides
minimal additional services over the IP layer, allowing great flexibility
in innovation for protocols tunnelled on top. Provided middleboxes do not
inspect the payload too carefully, the only real cost to innovation, when
compared to a native transport protocol running over IP, is a few bytes of
additional header. Examples in this space include RTP \cite{rfc:3550}, one
of the most widely deployed real-time transport protocols; the WebRTC Data
Channel \cite{draft-ietf-rtcweb-data-channel-13}, which tunnels
peer-to-peer SCTP associations over a DTLS association over UDP; and QUIC
\cite{draft-tsvwg-quic-protocol-02}, which provides a modern alternative 
to TCP, implemented over UDP.

@@

Evidence that these services can be deployed above UDP exists in the form
of the WebRTC data channel \cite{draft-ietf-rtcweb-data-channel-13}.  
\todo{expand}

@@

Taken together, the wide experiences with the WebRTC Data Channel and QUIC
demonstrate that the transport services necessary to support real-time
traffic could be deployed running over UDP. Our work prototyping the TCP
Hollywood protocol, and earlier measurements by Honda \emph{et al}.\
\cite{honda:2011:extend-tcp} also suggest that deployment over TCP is
possible.
